MS Depression Paper, post replication, started 2022 09 21

### 2023-09-29 Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd
with sensitivity analysis removing meds

@@

>>>>

[x] sensitivity analysis removing people on methylpred/pred/interferone B (lose 20 people, 5% of sample; MS+Dep = 221 (-11, 4.7%); MS-Dep = 139(-9, 6%))

    -Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.070-0.10, P <0.001)
    -Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
    -Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)

@@

#repeat analysis but remove people on neuroactive MS meds
```{r depression_vs_healthy_overall_volume_of_fascicles_affected_noifnbeta_steroids}
## compare disease within and outside depression network, between diagnoses, and interactions

  #remove people on ms medications that are known to worsen mood
 # filter(!str_detect(Medication, 'INTERFERON|PREDNISONE|METHYLPREDNISOLONE')) %>% 
  #filter(!str_detect(Medication, 'INTERFERON')) %>%
  filter(!str_detect(Medication, 'PREDNISONE')) %>%
 # filter(!str_detect(Medication, 'METHYLPREDNISOLONE')) %>%
  ungroup()

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  dplyr::select(subject, Diagnosis, Dep_network, Nondep_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#diagnosis: Dep > nondep T = 2.0, p = 0.046; Network dep>nondep = T=12.3, p = 2*10^-16; intx = T = 1.89, p = 0.06
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

#Diagnosis: MS+ > MS- 0.001-0.9; Network dep>nondep -.104--.078; intx: -0.040--0.00
confint(diagnosis_by_network_interaction_lmer)

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.070-0.10, P <0.001)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
#Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)
